SMT-Boosted Security Types for Low-Level MPC

### 2025-11-13 toplas26/sty.tex
checkpoint

\begin{definition}
  Given $\prog,\Gamma,R$ where $\secrets(\prog) = S$ and:
  $$
  \Gamma = \setit{[\phi_1^1,\phi_1^2] : \sharety, \ldots, [\phi_n^1,\phi_n^2] : \sharety}
  \cup \setit{\pubx{\phi_1} : \pubty,\ldots,\pubx{\phi_j} : \pubty} \cup
  \setit{\pubx{\phi^o_1} : \outty,\ldots,\pubx{\phi^o_k} : \outty}
  $$
  Then we write $\prog,\Gamma,R : {OK}$ iff all of the following conditions
  hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item For all $a,b \in \setit{1,2}$ we have
    $
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi^o_1,\ldots,\phi^o_k}}
    = 
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi_1^b,\ldots,\phi_n^b} \cup
      \setit{\phi_1,\ldots,\phi_j} \setit{\phi^o_1,\ldots,\phi^o_k}}
    $.
  \item For all $a,b \in \setit{1,2}$and $0 < i \le n$ we have
    $\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\phi_i^1 + \phi_i^2}} =
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\phi_i^1 + \phi_i^2, \phi_i^a}}$
  \item  For all $a,b \in \setit{1,2}$ and $0 < i \le n$, if
    $\toeq{\prog} \models \phi_i^a \eop \rx{w}{\cid_a} \wedge \phi_i^b \eop \phi - \rx{w}{\cid_a}$ for
    some $\phi$ and $\rx{w}{\cid_a}$ then $\rx{w}{\cid_a} \in R$.
  \item For all $0 < i \le j$, if $\toeq{\prog} \models \phi_i \eop \phi + \rx{w}{\cid_{\oid}}$ for
    some $\phi$  and $\rx{w}{\cid_{\oid}}$ then $\rx{w}{\cid_{\oid}} \in R$.
  \end{enumerate} 
\end{definition}

@@

>>>>

\begin{definition}
  Given $\prog,\Gamma,R$ where $\secrets(\prog) = S$ and:
  $$
  \Gamma = \setit{[\phi_1^1,\phi_1^2] : \sharety, \ldots, [\phi_n^1,\phi_n^2] : \sharety}
  \cup \setit{\pubx{\phi_1} : \pubty,\ldots,\pubx{\phi_j} : \pubty} \cup
  \setit{\pubx{\phi^o_1} : \outty,\ldots,\pubx{\phi^o_k} : \outty}
  $$
  Then we write $\prog,\Gamma,R : {OK}$ iff all of the following conditions
  hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item For all $a,b \in \setit{1,2}$ we have
    $
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi^o_1,\ldots,\phi^o_k}}
    = 
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \setit{\phi_1^b,\ldots,\phi_n^b} \cup
      \setit{\phi_1,\ldots,\phi_j} \setit{\phi^o_1,\ldots,\phi^o_k}}
    $.
  \item For all $a,b \in \setit{1,2}$ and $0 < i \le n$ we have
    $\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\phi_i^1 + \phi_i^2}} =
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{\setit{\phi_i^1 + \phi_i^2, \phi_i^a}}$
  \item  For all $a,b \in \setit{1,2}$ and $0 < i \le n$, if
    $\toeq{\prog} \models \phi_i^a \eop \rx{w}{\cid_a} \wedge \phi_i^b \eop \phi - \rx{w}{\cid_a}$ for
    some $\phi$ and $\rx{w}{\cid_a}$ then $\rx{w}{\cid_a} \in R$.
  \item For all $0 < i \le j$, if $\toeq{\prog} \models \phi_i \eop \phi + \rx{w}{\cid_{\oid}}$ for
    some $\phi$  and $\rx{w}{\cid_{\oid}}$ then $\rx{w}{\cid_{\oid}} \in R$.
  \end{enumerate} 
\end{definition}

@@

\begin{definition}
  Given  $\prog,\Gamma,R  : {OK}$ and $\iov(\prog) = S \cup V \cup O$.
  Then $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $\Gamma,\toeq{\prog} \vdash [x,\phi] : \sharety$ if $C = \setit{1}$
  or  $\Gamma,\toeq{\prog} \vdash [\phi,x] : \sharety$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$.
\end{definition}

\begin{theorem}
  If $\toeq{\prog} \vdash \varnothing,\varnothing \stredx \Gamma,R$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
